Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Changed title of 3.1

\subsection{== À réintégrer depuis ancienne section 4 ==}
We select two deep-learning-based NER models available in packaged software libraries: SpaCy NLP pipelines and CamemBERT.

>>>>

\subsection{== À réintégrer depuis ancienne section 4 ==}

A introduire en disant quo'n chercher à utiliser au plus des modèles simples à reprendre: déjà entraînés, dispos pour du français et adaptables
We select two deep-learning-based NER models available in packaged software libraries: SpaCy NLP pipelines and CamemBERT.
